SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-06-28 scipy-1.0/paper.tex
Converted figures to vector format

% Packages
\usepackage[super]{nth}
\usepackage{rotating}
\usepackage{makecell}
\usepackage{pifont}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{float}
\usepackage{pgfplotstable}
\usepackage[multiple]{footmisc}
\usepackage{booktabs,siunitx}

@@

SciPy provides fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks while interacting well with other packages specialized in that area.
For example, SciPy provides what one expects to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while 
Statsmodels\cite{statsmodels2010} provides
more advanced statistical estimators and inference methods;
scikit-learn\cite{pedregosa2011scikit} covers machine learning; and
PyMC3\cite{10.7717/peerj-cs.55}, emcee\cite{2013PASP-emcee} and 
PyStan\cite{pystan-ref} cover Bayesian statistics and probabilistic modeling.
scikit-image\cite{vanderwalt2014scikit} provides image processing
capabilities beyond SciPy's \texttt{ndimage}, SymPy\cite{meurer2017sympy}
provides a Python interface for symbolic computation, and
while \texttt{sparse.csgraph} or \texttt{spatial} offers basic tools
for working with graphs and networks compared to a more specialized
Python library like NetworkX\cite{hagberg2008networkx}.

@@

The \texttt{scipy.stats} subpackage contains more than 100 probability
distributions: 96 continuous and 13 discrete univariate distributions
and 10 multivariate distributions. The implementation relies on a
consistent framework that provides methods to sample random variates,
to evaluate the cumulative distribution function (CDF) and the probability
density function (PDF) and to fit parameters for every distribution.
Generally, the methods rely on specific implementations for each
distribution such as a closed form expression of the CDF or a sampling
algorithm, if available. Otherwise, default methods are used
based on generic code, e.g., numerical integration of the PDF to
obtain the CDF.
Key recent distributions added to \texttt{scipy.stats} include the
histogram-based distribution in \texttt{scipy.stats.rv\_histogram}
and the multinomial distribution in \texttt{scipy.stats.multinomial}
(used, for example, in natural language processing, see
\cite{Griffiths5228}).

>>>>

% Packages
\usepackage[super]{nth}
\usepackage{rotating}
\usepackage{makecell}
\usepackage{pifont}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{float}
\usepackage{pgfplotstable}
% \usepackage[multiple]{footmisc}
\usepackage{booktabs,siunitx}

@@

SciPy provides fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks while interacting well with other packages specialized in that area.
For example, SciPy provides what one expects to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while 
Statsmodels\cite{statsmodels2010} provides
more advanced statistical estimators and inference methods;
scikit-learn\cite{pedregosa2011scikit} covers machine learning; and
PyMC3\cite{10.7717/peerj-cs.55}, emcee\cite{2013PASP-emcee} and 
PyStan\cite{pystan-ref} cover Bayesian statistics and probabilistic modeling.
scikit-image\cite{vanderwalt2014scikit} provides image processing
capabilities beyond SciPy's \texttt{ndimage}, sympy\cite{meurer2017sympy}
provides a Python interface for symbolic computation, and
while \texttt{sparse.csgraph} or \texttt{spatial} offers basic tools
for working with graphs and networks compared to a more specialized
Python library like NetworkX\cite{hagberg2008networkx}.

@@

The \texttt{scipy.stats} subpackage contains more than 100 probability
distributions: 96 continuous and 13 discrete univariate distributions
and 10 multivariate distributions. The implementation relies on a
consistent framework that provides methods to sample random variates,
to evaluate the cumulative distribution function (cdf) and the probability
density function (pdf) and to fit parameters for every distribution. 
Generally, the methods rely on specific implementations for each
distribution such as a closed form expression of the cdf or a sampling 
algorithm, if available. Otherwise, default methods are used
based on generic code, e.g., numerical integration of the pdf to
obtain the cdf. 
Key recent distributions added to \texttt{scipy.stats} include the
histogram-based distribution in \texttt{scipy.stats.rv\_histogram}
and the multinomial distribution in \texttt{scipy.stats.multinomial}
(used, for example, in natural language processing, see
\cite{Griffiths5228}).
